ODGI: understanding pangenome graphs

### 2021-10-29 manuscript/main.tex
typo
draft odgi untangle

Figure showing the untangling of C4 (Fig. \ref{fig:odgi_viz}\textbf{f-g})
Figure showing tips over a single human chromosome from HPRC.

>>>>

To obtain a more precise overview of collapsed \textit{loci}, we can apply \textit{odgi untangle} to segment paths into linear segments by breaking these segments where the paths loop back on themselves.
In this way, we can obtain base-level information on the copy number status of the sequences in the locus.

Figure showing the untangling of C4 (Fig. \ref{fig:odgi_viz}\textbf{h})
Figure showing tips over a single human chromosome from HPRC.
